---
title: "BURST Statistical Final Report"
author: "Inge Christoffer Olsen, PhD"
date: '`r format(Sys.time(), "%d %B, %Y")` '
output:
  word_document:
    reference_docx: report_template.docx
    toc: yes
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    df_print: paged
params:
  viedoc_export: _20230919_063242
  bibliography: data/misc/grateful-refs.bib
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(wesanderson)
library(rlang)
library(glue)
library(knitr)
library(labelled)
library(rtables)
library(ggplot2)
library(lme4)
library(marginaleffects)
library(flextable)

```

```{r load-datasets, include = FALSE}

raw <- read_rds("data/raw/raw.rds")
adsl <- read_rds("data/ad/adsl.rds")
adran_wide <- readr::read_rds("data/ad/adran_wide.rds")
adsl_all <- read_rds("data/ad/adsl_all.rds")
addm <- read_rds("data/ad/addm.rds")
adprom <- read_rds("data/ad/adprom.rds")
source("src/external/functions.R", local = knitr::knit_global())
export_date = substr(params$viedoc_export,2,9) %>% lubridate::as_datetime()

#pr_text = "While the results are based on real data, the treatment allocation has been drawn randomly for this report. Thus, this is a mock-up report intended to show how the final report will look like, without showing the actual results of the trial and the treatment differences."

pr_text = "The results in this report is according to the true random allocation. "

```
# Introduction
This is the report for the first interim analysis of the BURST trial. The data are based on an export from the Viedoc electronic data capture at `r export_date` system time stamped "`r params$viedoc_export`". 

`r pr_text` 

There were `r n_distinct(adsl)` included patients of which `r n_distinct(adsl %>% filter(fas))` were randomised and included in the full analysis set. 

# Demographics

```{r f_dm}
s_summary <- function(x, .N_col) {
  if (is.numeric(x)) {
    in_rows(
      "n" = rcell(sum(!is.na(x)), format = "xx"),
      "Mean (sd)" = rcell(c(mean(x, na.rm = TRUE), sd(x, na.rm = TRUE)), format = "xx.xx (xx.xx)"),
      "IQR" = rcell(IQR(x, na.rm = TRUE), format = "xx.xx"),
      "min - max" = rcell(range(x, na.rm = TRUE), format = "xx.xx - xx.xx")
    )
  } else if (is.factor(x)) {
   in_rows(.list = lapply(as.list(table(x)), function(xi) rcell(xi * c(1, 1/.N_col), format = "xx (xx.xx%)")))
  } else {
    in_rows(.list = as.list(table(factor(x))))
  }
}


dmvars <- names(addm %>% select(-subjectid, -fas))
dmlabs <- var_label(addm %>% select(-subjectid, -fas), unlist = TRUE)

```

## All randomised

```{r dm_tbl_all}
dmlyt <- basic_table(show_colcounts = TRUE, title = "Demographics and baseline characteristics", subtitles = "All included") %>%
  analyze(dmvars , afun = s_summary, var_labels = dmlabs)

dm_tbl_all <- build_table(dmlyt, addm) %>%
  tt_to_flextable() %>%
  autofit()
dm_tbl_all

```

## Excluded from FAS

```{r dm_tbl_ex}
dmlyt <- basic_table(show_colcounts = TRUE, title = "Demographics and baseline characteristics", subtitles = "Excluded before randomisation") %>%
  analyze(dmvars , afun = s_summary, var_labels = dmlabs)

dm_tbl_all <- build_table(dmlyt, addm %>% filter(!fas)) %>%
  tt_to_flextable() %>%
  autofit()
dm_tbl_all

```
## Full analysis set

```{r dm_tbl_fas}

dmlyt <- basic_table(show_colcounts = TRUE, title = "Demographics and baseline characteristics", subtitles = "Full analysis set (randomised)") %>%
  analyze(dmvars , afun = s_summary, var_labels = dmlabs)

dm_tbl <- build_table(dmlyt, addm %>% filter(fas)) %>% 
  tt_to_flextable() %>% 
  autofit()
dm_tbl

```
## Pain etc at baseline

```{r painbl_tbl_fas}

painvars <- names(adprom %>% select(painleg1:hscl_score, isi_score))
painlabs <- var_label(adprom %>% select(painleg1:hscl_score, isi_score), unlist = TRUE)



painbl_cont <- adprom %>% 
  filter(fas) %>% 
  filter(period == 0) %>% 
  group_by(subjectid) %>% 
  summarise(across(all_of(painvars), ~ mean(.x, na.rm = TRUE))) %>% 
  mutate(hscl_score_cat = cut(hscl_score, c(0,1.76, 100), c("HSCL ≤ 1.75", "HSCL > 1.75")),
         isi_score_cat = cut(isi_score, c(7.5, 14.5, 28.5), c("ISI 8-14", "ISI 15-28"))) %>% 
  set_variable_labels(hscl_score_cat = "HSCL score categorised at 1.75", 
                      isi_score_cat = "ISI score categorised at 15")

painvars <- names(painbl_cont %>% select(-subjectid))
painlabs <- c(painlabs,"HSCL score categorised at 1.75", "ISI score categorised at 15")


bllyt <- basic_table(show_colcounts = TRUE, title = "Mean pain etc at baseline", subtitles = "Full analysis set (randomised)") %>%
  analyze(painvars , afun = s_summary, var_labels = painlabs)

dm_tbl <- build_table(bllyt, painbl_cont) %>% 
  tt_to_flextable() %>% 
  autofit()
dm_tbl

```


# Treatment information

```{r}

kn <- raw %>% 
  pick("kn") %>% 
  select(subjectid, eventseq, eventid, eventdate, amp = kntvlig1, imp = kntotim) %>% 
  set_variable_labels(amp = "Amplitude for sensory treshold",
                      imp = "Impedance") %>% 
  filter(eventid != "V00_1") %>% 
  filter(eventid != "V07")

sc <- raw %>% 
  pick("sc") %>% 
  select(subjectid, eventid, last_amp = sc_forrige) %>% 
  mutate(eventid = case_when(
    eventid == "V02" ~ "V01",
    eventid == "V03" ~ "V02",
    eventid == "V04" ~ "V03",
    eventid == "V05" ~ "V04",
    eventid == "V06" ~ "V05",
    eventid == "V07" ~ "V06"
  )) %>% 
  set_variable_labels(last_amp = "Stimulation Amplitude from previous period") 

ti <- adran_wide %>% 
  filter(adherent) %>% 
  left_join(kn, by = "subjectid") %>% 
  left_join(sc, by = c("subjectid", "eventid")) %>% 
  mutate(rantrt = case_when(
    eventdate <= eventdate1 ~ rantrt1,
    eventdate <= eventdate2 ~ rantrt2,
    eventdate <= eventdate3 ~ rantrt3,
    eventdate <= eventdate4 ~ rantrt4,
    eventdate <= eventdate5 ~ rantrt5,
    eventdate <= eventdate6 ~ rantrt6,
    TRUE ~ "Follow-up"
  )) %>% 
  mutate(period = case_when(
    eventdate <= eventdate1 ~ 1,
    eventdate <= eventdate2 ~ 2,
    eventdate <= eventdate3 ~ 3,
    eventdate <= eventdate4 ~ 4,
    eventdate <= eventdate5 ~ 5,
    eventdate <= eventdate6 ~ 6,
    eventdate <= eventdate7 ~ 7,
    TRUE ~ 7
  )) %>% 
  mutate(pair = paste0("Pair ", ceiling(period / 2))) %>% 
  mutate (pair = if_else(pair == "Pair 0", "Baseline", pair)) %>% 
  select(-c(eventdate1:eventdate7, rantrt1:rantrt7, trtdose1:trtdose7))

```



## Amplitude for sensory threshod

```{r}


f_antbl3_period <- function(data, var) {
  label_ <- labelled::var_label(data[[var]])
  data <- data %>% 
    mutate(period = factor(period))
  
  lyt <- rtables::basic_table(subtitles = c("Period", "Full analysis set", label_)) %>%
    split_cols_by("period", split_label = "Period") %>% 
    split_rows_by("subjectid") %>% 
    analyze(var , afun = mean, var_label = "")
  
  prom_tbl_all <- build_table(lyt, data) %>% 
    tt_to_flextable() %>% 
    autofit()
  
    return(prom_tbl_all)
}
```

```{r}

f_antbl3_period(ti, "amp")

```

## Impedance
```{r}

f_antbl3_period(ti, "imp")

```

## Stimulation Amplitude as set before treatment period
```{r}

f_antbl2_period(adprom, "trtdose")

```

## Stimulation amplitude as registered after treatment period

```{r}

f_antbl2_period(ti, "last_amp")

```



# Analysis


## Primary outcome: Usual pain intensity in lower extremity (NRS) 
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7}
f_anplot1(adprom, "painleg3")

```

### Descriptive table

```{r }

f_antbl_period(adprom, "painleg3")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "painleg3")
res$tbl

```
Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.



### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed(adprom, "painleg3")
qqnorm(residuals(res$fit))
 
```


By subject
```{r}
res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

Overall
```{r}
res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)

res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```


## Secondary outcome: Highest pain intensity in lower extremity (NRS) 
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7}
f_anplot1(adprom, "painleg1")

```

### Descriptive table

```{r}

f_antbl_period(adprom, "painleg1")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "painleg1")
res$tbl

```
Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.



### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed(adprom, "painleg1")
qqnorm(residuals(res$fit))
 
```

By subject
```{r}

res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

By treatment and Overall
```{r}
res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)

res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```



## Secondary outcome: Lowest pain intensity in lower extremity (NRS) 
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7}
f_anplot1(adprom, "painleg2")

```

### Descriptive table

```{r }

f_antbl_period(adprom, "painleg2")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "painleg2")
res$tbl

```
Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.



### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed(adprom, "painleg2")
qqnorm(residuals(res$fit))
 
```


By subject
```{r}

res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

By treatment and overall
```{r}
res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)

res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```




## Secondary outcome: Current pain intensity in lower extremity (NRS) 
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7}
f_anplot1(adprom, "painleg4")

```

### Descriptive table

```{r }

f_antbl_period(adprom, "painleg4")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "painleg4")
res$tbl

```
Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.



### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed(adprom, "painleg4")
qqnorm(residuals(res$fit))
 
```

By subject
```{r}

res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

By treatment and overall
```{r}
res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)

res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```




## Secondary outcome: Usual pain intensity in the back (NRS) 
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7, warning = FALSE}
f_anplot1(adprom, "painback")

```

### Descriptive table

```{r, warning = FALSE}

f_antbl_period(adprom, "painback")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "painback")
res$tbl

```
Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.



### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed(adprom, "painback")
qqnorm(residuals(res$fit))
 
```

By subject
```{r}

res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

By treatment and overall
```{r}
res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)

res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```




## Secondary outcome: Pain unpleasantness (NRS) 
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7, warning = FALSE}
f_anplot1(adprom, "painunpl")

```

### Descriptive table

```{r }

f_antbl_period(adprom, "painunpl")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "painunpl")
res$tbl

```
Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.



### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed(adprom, "painunpl")
qqnorm(residuals(res$fit))
 
```


By subject
```{r}

res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

By treatment and overall
```{r}
res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)

res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```




## Secondary outcome: Ability to do first activity (NRS) 
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7, warning=FALSE}
f_anplot1(adprom, "psfs1")

```

### Descriptive table

```{r }

f_antbl_period(adprom, "psfs1")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "psfs1")
res$tbl

```
Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.



### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed(adprom, "psfs1")
qqnorm(residuals(res$fit))
 
```


By subject
```{r}

res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

By treatment and overall
```{r}
res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)

res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```






## Secondary outcome: Ability to do second activity (NRS) 
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7, warning = FALSE}
f_anplot1(adprom, "psfs2")

```

### Descriptive table

```{r }

f_antbl_period(adprom, "psfs2")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "psfs2")
res$tbl

```
Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.



### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed(adprom, "psfs2")
qqnorm(residuals(res$fit))
 
```

By subject
```{r}
res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

By treatment group and overall
```{r}
res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)

res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```



## Secondary outcome: Ability to do third activity (NRS) 
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7, warning=FALSE}
f_anplot1(adprom, "psfs3")

```

### Descriptive table

```{r }

f_antbl_period(adprom, "psfs3")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "psfs3")
res$tbl

```
Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.



### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed(adprom, "psfs3")
qqnorm(residuals(res$fit))
 
```

By subject
```{r}

res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

By treatment and overall
```{r}
res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)

res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```



## Secondary endpoint: Insomnia Severity Index questionnaire total score
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7, warning = FALSE}
f_anplot1(adprom, "isi_score")

```
### Descriptive table

```{r }

f_antbl2_period(adprom, "isi_score")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "isi_score")

res$tbl

```

Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.

### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed2(adprom, "isi_score")
qqnorm(residuals(res$fit))
 
```

By subject
```{r}

res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

By treatment and overall
```{r}

res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)


res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```





## Secondary endpoint: EQ-5D-5L Utility Index 
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7, warning = FALSE}
f_anplot1(adprom, "eq5dui")

```
### Descriptive table

```{r }

f_antbl2_period(adprom, "eq5dui")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "eq5dui")

res$tbl

```

Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.

### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed3(adprom, "eq5dui")
qqnorm(residuals(res$fit))
 
```

By subject
```{r}

res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

By treatment and overall
```{r}

res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)

res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```




## Secondary endpoint: EQ-5D-5L self-rated health (VAS)
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7, warning = FALSE}
f_anplot1(adprom, "eq5dvas")

```
### Descriptive table

```{r }

f_antbl2_period(adprom, "eq5dvas")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "eq5dvas")

res$tbl

```

Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.

### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed3(adprom, "eq5dvas")
qqnorm(residuals(res$fit))
 
```

By subject
```{r}

res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

By treatment and overall
```{r}
res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)

res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```


## Secondary endpoint: Patient Global Impression of Change

### Descriptive table

```{r }
prevtrt <- adprom %>% 
  select(subjectid, rantrt, period) %>% 
  unique()

prevtrt <- prevtrt %>% 
  group_by(subjectid) %>% 
  mutate(prevtrt = lag(rantrt)) %>% 
  select(-rantrt)

db_change <- adprom %>% 
  left_join(prevtrt, by = c("subjectid", "period")) %>% 
  select(subjectid, rantrt, prevtrt, period, pgic, pgiccd) %>% 
  filter(rantrt != "Baseline" & !is.na(pgic)) %>% 
  mutate(transition = paste0(prevtrt, " - ", rantrt)) %>% 
  mutate(transition = factor(transition))

lyt <- basic_table(subtitles =c("Full analysis set", "Patient Global Impression of Change")) %>% 
  split_cols_by("transition") %>% 
  analyze("pgic", afun = s_summary)

  tbl_change <- build_table(lyt, db_change) %>% 
    tt_to_flextable() %>% 
    autofit()
  
  tbl_change

```

### Hypothesis test and treatment effect estimates

```{r, warning = FALSE, include = FALSE}

analyse_change <- db_change %>% 
  filter(transition == "Burst stimulation - Sham" | transition == "Sham - Burst stimulation") %>% 
  mutate(transition = factor(transition))


fit_change <- lmer(pgiccd ~ transition + (1|subjectid), data = analyse_change)


```

```{r}
analyse_change %>% 
  group_by(transition) %>% 
  summarise(mean = mean(pgiccd), sd = sd(pgiccd)) %>% 
  kable(col.names = c("", "Mean", "SD"))

 avg_comparisons(fit_change, variables = "transition") %>% 
   broom::tidy() %>% 
   select(-term,  -starts_with("predicted"), -statistic) %>% 
   kable(digits = 3)
```




## Secondary outcome: Patient blinding question
### Descriptive table by participant

```{r}
db_blinding <- adprom %>% 
  filter(rantrt != "Baseline" & !is.na(pbqcd)) %>%
  select(subjectid, rantrt, period, pair,pbq, pbqcd) %>% 
  mutate(pbq_ = as.character(pbq))



f_antbl_period(db_blinding, "pbq")


```

```{r}

lyt <- basic_table(subtitles =c("Full analysis set", "Patient Blinding Quesiton")) %>% 
  split_cols_by("rantrt") %>% 
  analyze("pbq", afun = s_summary) 
  
tbl_blind <- build_table(lyt, db_blinding) %>% 
    tt_to_flextable() %>% 
    autofit()

tbl_blind


```
```{r, include = FALSE}
chisq <-  chisq.test(db_blinding$rantrt, db_blinding$pbqcd)
fisher <-  fisher.test(db_blinding$rantrt, db_blinding$pbqcd)

```
P-value of the null hypothesis chi-squared test: `r format.pval(chisq$p.value, digits = 2, eps = 0.001)`. 

P-value of the null hypothesis Fisher test: `r format.pval(fisher$p.value, digits = 2, eps = 0.001)`. 




## Secondary endpoint: Hopkins Symptom Checklist-25 mean score
### Plot
```{r, fig.fullwidth = TRUE, fig.width = 10, fig.height = 7, warning = FALSE}
f_anplot1(adprom, "hscl_score")

```
### Descriptive table

```{r }

f_antbl2_period(adprom, "hscl_score")

```

### Hypothesis test

```{r}

res <- f_antbl_overall(adprom, "hscl_score")

res$tbl

```

Values are Burst stimulation - Sham.


P-value of the null hypothesis test: `r format.pval(res$t.test$p.value, digits = 2, eps = 0.001)`.

### Treatment effect estimates

QQ-plot
```{r}
res <- f_mixed3(adprom, "hscl_score")
qqnorm(residuals(res$fit))
 
```

By subject
```{r}

res$by_subj %>% 
  knitr::kable(col.names = c("Subject ID", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
 
```

By treatment and overall
```{r}

res$by_trt %>% 
  knitr::kable(col.names = c("Treatment", "Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)

res$overall %>% 
  knitr::kable(col.names = c("Estimate", "Std. Err.", "p-value", "Lower CL", "Upper CL"), digits = 3)
```

## Carry over effect

First fit the model:
```{r}
prevtrt <- adprom %>% 
  select(subjectid, rantrt, period) %>% 
  unique()

prevtrt <- prevtrt %>% 
  group_by(subjectid) %>% 
  mutate(prevtrt = lag(rantrt)) %>% 
  select(-rantrt)

data <- adprom %>% 
  left_join(prevtrt, by = c("subjectid", "period")) %>% 
  filter(rantrt != "Baseline") %>% 
  mutate(prevtrt = if_else(prevtrt == "Baseline", "Sham", prevtrt)) %>% 
  mutate(rantrt = factor(rantrt),
         pair = factor(pair),
         prevtrt = factor(prevtrt))

fit8<- lmer(painleg3 ~ rantrt + pair + prevtrt  + prevtrt:rantrt + (1|subjectid) + (1|subjectid:pair) + (1|subjectid:rantrt), data = data)


summary(fit8)


```
Then plot the expected outcome by current and previous treatment:
```{r}
tmp <- hypotheses(fit8) %>% 
  tidy() 

###
# To show that the next expression gives results as expected. 
# p <-predictions(fit8, newdata = datagrid(rantrt = c("Sham", "Burst stimulation"), prevtrt = c("Sham", "Burst stimulation"), grid_type = "counterfactual"))
# p %>% group_by(prevtrt, rantrt) %>% summarise(estimate = mean(estimate))
# aggregate(estimate ~ rantrt + prevtrt + rantrt:prevtrt, data = p, FUN = mean)

avg_predictions(fit8, newdata = datagrid(rantrt = c("Sham", "Burst stimulation"), prevtrt = c("Sham", "Burst stimulation"), grid_type = "counterfactual"), by = c( "prevtrt", "rantrt")) %>% 
  tidy() %>% 
  kable(caption = "Outcome by tretment and previous treatment", digits = 3)



```

Then compute the treatment effect estimate by previous treatment:

```{r}
avg_comparisons(fit8, variables = "rantrt", newdata = datagrid(rantrt = c("Sham", "Burst stimulation"), prevtrt = c("Sham", "Burst stimulation"), grid_type = "counterfactual"), by = c("prevtrt")) %>% 
  tidy() %>%  
  select(-term,  -starts_with("predicted"), -statistic) %>% 
  kable(digits = 3)


```

Finally see if there is a difference:
```{r}
cmp <- avg_comparisons(fit8, variables = "rantrt", newdata = datagrid(rantrt = c("Sham", "Burst stimulation"), prevtrt = c("Sham", "Burst stimulation"), grid_type = "counterfactual"), by = c("prevtrt"))
hypotheses(cmp, hypothesis = "pairwise") %>% 
  tidy() %>% 
  select(-term,  -starts_with("predicted"), -statistic) %>% 
  kable(digits = 3)

```




# Safety Analysis

```{r}
ko <- raw %>% 
  pick("ko") %>% 
  select(subjectid, eventdate, ko_dt, ko_spes, ko_annet)

adae <- adsl %>% 
  inner_join(ko, by = "subjectid") %>% 
  select(sitename, subjectid, paticdat, sex, age, ran1dt, randomised, fas, ko_dt, ko_spes, ko_annet)

labels <- var_label(adae, unlist = TRUE)

adae %>% 
  knitr::kable(col.names = labels)

```

# Parathesia Coverage

```{r}
isa <- raw %>% 
  pick("isa") %>% 
  select(subjectid, eventid, eventdate, starts_with("isa_"))

adsl %>% 
  filter(fas) %>% 
  left_join(isa, by = "subjectid") %>% 
  #mutate(par_leg = if_else(!is.na(isa_ben), as.character(isa_ben), as.character(isa_ben__2))) %>% 
  #mutate(par_back = if_else(!is.na(isa_rygg), as.character(isa_rygg), as.character(isa_rygg__2))) %>% 
  select(sitename, subjectid, par_leg = isa_ben, par_back = isa_rygg) %>% 
  knitr::kable(col.names = c("Site", "Subject ID", "Parathesia Coverage Leg", "Parathesia Coverage Back"))


  



```
# Listings

```{r}

op <- raw %>% 
  pick("op") %>% 
select(subjectid,  eventid, eventdate, opmedend, opmedspe1, opmed7d, opmedspe, opbehov, opmedds, oppattro, opsimcom, oppatsim, op1, oppatbiv, opbivspe, opsvikt, optekspe) 

listing <- adsl %>% 
  select(subjectid, fas) %>% 
  filter(fas) %>% 
  left_join(adran_wide, by = "subjectid") %>% 
  select(-starts_with("trtdose")) %>% 
  left_join(op, by = "subjectid") %>% 
   mutate(rantrt = case_when(
    eventdate <= eventdate1 ~ "Baseline",
    eventdate <= eventdate2 ~ rantrt1,
    eventdate <= eventdate3 ~ rantrt2,
    eventdate <= eventdate4 ~ rantrt3,
    eventdate <= eventdate5 ~ rantrt4,
    eventdate <= eventdate6 ~ rantrt5,
    eventdate <= eventdate7 ~ rantrt6,
    TRUE ~ "Follow-up"
  ))%>% 
  mutate(period = case_when(
    eventdate <= eventdate1 ~ 0,
    eventdate <= eventdate2 ~ 1,
    eventdate <= eventdate3 ~ 2,
    eventdate <= eventdate4 ~ 3,
    eventdate <= eventdate5 ~ 4,
    eventdate <= eventdate6 ~ 5,
    eventdate <= eventdate7 ~ 6,
    TRUE ~ 7
  )) %>% 
  mutate(pair = paste0("Pair ", ceiling(period / 2))) %>% 
  mutate (pair = if_else(pair == "Pair 0", "Baseline", pair)) %>% 
  mutate(studyday = eventdate - ran1dt) %>% 
  group_by(subjectid) %>% 
  mutate(subject = paste0("Subject ",  stringr::str_pad(cur_group_id(), 2, pad="0"))) %>% 
  ungroup()  %>%  
  select(-c(eventdate1:eventdate7, rantrt1:rantrt7)) %>% 
   select(subject, subjectid:adherent, studyday, rantrt,  period, pair, everything()) 
```


## Analgetica
```{r}
listing %>% 
  filter(eventid != "V01") %>% 
  select(subjectid, studyday, rantrt, period, pair, opmedend, opmedspe1, opmed7d, opmedspe, opbehov, opmedds) %>% 
  knitr::kable(col.names = c("Subject", "Studyday", "Treatment", "Period", "Pair", "Changed analgetica since last control?", "Specify", "Changed analgetica last 7 days", "Specify", "Any other use of analgetica last 7 days?", "Specify"))
```

## Adverse reactions to the stimulation

```{r}
listing %>% 
  filter(eventid != "V01") %>% 
  select(subjectid, studyday, rantrt, period, pair, oppatbiv, opbivspe) %>% 
  knitr::kable(col.names = c("Subject", "Studyday", "Treatment", "Period", "Pair", "Any adverse reactions last 14 days?", "Specify"))

```
## Technical problems
```{r}
listing %>% 
  filter(eventid != "V01") %>% 
  select(subjectid, studyday, rantrt, period, pair, opsvikt, optekspe) %>% 
  knitr::kable(col.names = c("Subject", "Studyday", "Treatment", "Period", "Pair", "Any technical problems last 14 days?", "Specify"))
```

# Suppementary Materials

```{r}
#report::cite_packages(cite.tidyverse = TRUE, output = "paragraph", out.dir = "data/misc") 
pkgs <- report::cite_packages(output = "table", out.dir = ".")
knitr::kable(pkgs)
```



